Analysing Constraint Grammar with a SAT solver

### 2015-10-18 paper/lrec/eval_futurework.tex
more text
more text/pictures

>>>>

We tested three grammars for rules that cannot apply. The smallest grammar was Dutch, with 68 rules; second was Spanish with 279 rules, and the largest was Finnish, with 1185 rules.
For the smaller grammars, we were able to verify manually that the results hold.

\begin{table}[]
\centering
\begin{tabular}{|l|l|l|l|}
\hline
                         & \textsc{nld}  & \textsc{spa}  & \textsc{fin}  \\ \hline
Rules in grammar      & 68              & 279               & 1185              \\ \hline
Redundant rules found & 1               & ???               & ???    \\ \hline
Running time          & n sec           & ??? min           & ??? h    \\ \hline
\end{tabular}
\caption{Results}
\label{table:res}
\end{table}

### 2015-10-18 paper/lrec/implementation.tex
more text/pictures

@@

\begin{table*}[]
\centering
\caption{SAT-encoding of \texttt{REMOVE v IF (-1 det)} applied to \emph{the bear}}
\label{table:vars}
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Word} & \textbf{Variables}                                                          & \textbf{Default rules}               & \textbf{Constraint rules}                                  \\ \hline
``the''         & \texttt{the\_det}                                                           & \texttt{the\_det}                    & \multirow{2}{*}{\texttt{the\_det}  $\Rightarrow$ $\neg$\texttt{bear\_v\_pl}} \\ \cline{1-3}
``bear''        & \begin{tabular}[c]{@{}l@{}}\texttt{bear\_n\_sg} \\ \texttt{bear\_v\_pl}\end{tabular} & \texttt{bear\_n\_sg} $\vee$ \texttt{bear\_v\_pl} &                                                            \\ \hline
\end{tabular}
\end{table*}

@@

All rules are applied to all word, given that their context is in scope: for instance, the sentence-initial word doesn't meet any condition that requires something of previous words.
However, being a condition for another target will also shape a word.
At a level of real texts, a rule such as \texttt{REMOVE b IF (-1 a)} is an instruction to remove a \texttt{b} if we find an \texttt{a} before it.
In case of a symbolic sentence, we start in a situation where every word can be an \texttt{a} or \texttt{b}. In that context, the rule behaves as a statement about that \texttt{b} may not follow \texttt{a}. This relation is encoded between all adjacent words, and each of them can follow the restriction in the way that is compliant with other rules.
For instance, word 1 may be constrained by another rule to have no \texttt{a}, and this means that word 2 is free to have \texttt{b} or not have it. If word 3 is required to have an  \texttt{a}, then word 4 either has to have no \texttt{b}, or it has to have only \texttt{b}, by the rule that the last analysis of the word will not be removed.

>>>>

\begin{table*}[]
\centering
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Word} & \textbf{Variables}                                                          & \textbf{Default rules}               & \textbf{Constraint rules}                                  \\ \hline
``the''         & \texttt{the\_det}                                                           & \texttt{the\_det}                    & \multirow{2}{*}{\texttt{the\_det}  $\Rightarrow$ $\neg$\texttt{bear\_v\_pl}} \\ \cline{1-3}
``bear''        & \begin{tabular}[c]{@{}l@{}}\texttt{bear\_n\_sg} \\ \texttt{bear\_v\_pl}\end{tabular} & \texttt{bear\_n\_sg} $\vee$ \texttt{bear\_v\_pl} &                                                            \\ \hline
\end{tabular}
\caption{SAT-encoding of \texttt{REMOVE v IF (-1 det)} applied to \emph{the bear}}
\label{table:vars}
\end{table*}

@@

@@

All rules are applied to all word, given that their context is in scope: for instance, the sentence-initial word doesn't meet any condition that requires something of previous words.
However, being a condition for another target will also shape a word.
At a level of real texts, a rule such as \texttt{REMOVE verb IF (-1 det)} is an instruction to remove a \texttt{verb} if we find a \texttt{det} before it.
In case of a symbolic sentence, we start in a situation where every word can be a \texttt{det} or a \texttt{verb}. In that context, the rule behaves as a broader constraint about every pair of two words \texttt{verb} may not follow \texttt{det}. This relation is encoded between all adjacent words, and each of them can follow the restriction in the way that is compliant with other rules.

\begin{figure}[]

\includegraphics[width=0.42\textwidth]{symbolic_sentence.png}

\caption{Symbolic sentence beginning to take shape}
\label{fig:example}
\end{figure}

% For instance, word 1 may be constrained by another rule to have no \texttt{det}, and this means that word 2 is free to have \texttt{verb} or not have it. If word 3 is required to have a  \texttt{det}, then word 4 either has to have no \texttt{verb}, or it has to have only \texttt{verb}, by the rule that the last analysis of the word will not be removed.
